Supplementary figures for Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis

### 2020-12-02 manuscript/manuscript.Rmd
supplementary tables added: treatment combinations and outcomes by hospital
More tweaks from feedback

---
title: "Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis" 
output: 
  #rticles::arxiv_article
  #pdf_document
  # bookdown::pdf_document2:
  #    toc: false
  bookdown::word_document2: 
    toc: false
    number_sections: false
    reference_docx: "output_template.docx"
abstract: |  
  **Abstract:** We collected a multi-centric retrospective dataset of patients who were admitted to 10 hospitals in Czech Republic and tested positive for SARS-CoV-2. The dataset contains baseline patient characteristics, breathing support required, pharmacological treatment received and multiple markers on daily resolution. Patients in the dataset were treated with hydroxychloroquine (N = 108), azithromycin (N = 72), favipiravir (N = 9), convalescent plasma (N = 7), dexamethasone (N = 4) and remdesivir (N = 3), often in combination. Most patients were admitted during the first wave of the epidemic. To explore association between treatments and patient outcomes we performed multiverse analysis, observing how the conclusions change between defensible choices of statistical model, predictors included in the model and other analytical degrees of freedom.  Weak evidence to constrain the potential efficacy of azithromycin and favipiravir can be extracted from the data. Additionally, we performed external validation of several proposed prognostic models for Covid-19 severity showing that they mostly perform unsatisfactorily on our dataset.
bibliography: Covid19.json
csl: journal-of-medical-virology.csl
date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
author: "`r { source(here::here('manuscript', 'authors.R')); get_authors_string() }`"
---

@@

The Covid-19 pandemic, caused by severe acute respiratory syndrome coronavirus (SARS-CoV-2) has, as of November 2020, led to over 46 million cases and over 1.1 million deaths. Proposed treatments include antivirals approved for other indications (chloroquine, hydroxychloroquine, lopinavir/ritonavir, remdesivir, favipiravir, umifenovir), azithromycin, corticosteroids, immunoglobulins, tocilizumab and convalescent plasma [@http://zotero.org/users/5567156/items/8XWTUMUI; @http://zotero.org/users/5567156/items/6Q8Z8VJR]. As of this writing, the only treatment that exhibited positive effects in randomized trials is the corticosteroid dexamethasone for severe cases [@http://zotero.org/users/5567156/items/IW6VZ53Q; @http://zotero.org/users/5567156/items/5VAKEW58]. Remdesivir, previously designed and approved for Ebola, SARS and MERS, is currently the only antiviral against SARS-CoV-2 approved by the FDA. However, during spring and summer it was available only in limited amounts via compassionate use programme. Randomized clinical trials on remdesivir have provided  conflicting evidence [@http://zotero.org/users/5567156/items/MFS3IPPU; @http://zotero.org/users/5567156/items/KB5UDZH3]. Despite initial promise, hydroxychloroquine has failed to show benefit for both hospitalized patients [@http://zotero.org/users/5567156/items/9X3UH8ZM; @http://zotero.org/users/5567156/items/KB5UDZH3], as an early treatment [@http://zotero.org/users/5567156/items/G6KZKVMI], as well as pre- and post-exposure prophylaxis [@http://zotero.org/users/5567156/items/7C23YCV5; @http://zotero.org/users/5567156/items/GMR9FX9Z; @http://zotero.org/users/5567156/items/H4CLJNUR]. Further, no improvement could be discerned when adding azithromycin to hydroxychloroquine therapy [@http://zotero.org/users/5567156/items/BQLRZGTQ]. Similarly, Lopinavir/Ritonavir did not show benefit [@http://zotero.org/users/5567156/items/6I6GAVWU]. No benefit was observed for convalescent plasma [@http://zotero.org/users/5567156/items/UEXLDJCB; @http://zotero.org/users/5567156/items/BHGT88US].

@@

Favipiravir is one of the less explored experimental treatments, previously used for influenza including avian types, with only one larger RCT in Covid- 19 known to us [@http://zotero.org/users/5567156/items/ISLSL7UC], the study however has many potentially severe problems [@http://zotero.org/users/5567156/items/7HDXLWEA]. Even considering studies or case series with only several treated patients, very few are available [@http://zotero.org/users/5567156/items/F3VNTQ92; @http://zotero.org/users/5567156/items/FSUQMUP8; @http://zotero.org/users/5567156/items/894H9N9B]. None of the results allow strong conclusions about benefits or harms of favipiravir, although a  metaanalysis of all available small studies showed an effect of favipiravir on clinical improvement in mild and moderate disease [@http://zotero.org/users/5567156/items/7595KBWR].

 For additional summary of treatments under investigation see [@http://zotero.org/users/5567156/items/YP62P6XJ].

@@

```{r progression, fig.cap="Disease progression for all patients included in the study as determined by breathing support required. Ventilated = any form of ventilation (non-invasive positive-pressure ventilation, mechanical ventilation and extra-corporeal membrane oxygenation)."}
my_paste <- function(x) {
  paste0(as.integer(x), collapse = "")
}

@@

As noted above, the nature of the convenience sample did not enforce random assignment of treatments to patients. In fact, patients with worse baseline characteristics, which lead to worse outcomes, were less likely to receive hydroxychloroquine (see Supplementary Figure 3). This clearly creates a bias towards a positive effect of hydroxychloroquine on the outcome (and potentially for other treatments as well - most were used in combination with hydroxychloroquine), which, however, could be false.

@@

Here, we focus on hydroxychloroquine and azithromycin as those are the only treatments with larger sample size. We also investigate favipiravir as it is less well reported in the literature. Hydroxychloroquine was dosed almost exclusively in a 5-day regime starting with a loading dose of 800mg on the first day and followed by 400mg. Majority of patients complemented hydroxychloroquine with azithromycin while azithromycin was rarely used alone (see Table \@ref(tab:summarytable)). Azithromycin was most frequently dosed 250 or 500mg/day, but doses ranging from 100mg/day to 1500 mg/day were observed.  Favipiravir was used only at one site with a loading dose of 3600mg on the first day, followed by at most 9 days with a 1600mg dose. All but one of the patients receiving favipiravir also received hydroxychloroquine. Treatment was initiated mostly within two days of admission (see Supplementary Figure 2).

The results of the multiverse analysis for association between hydroxochloroquine, azithromycin and favipiravir usage and death is shown in Figure&nbsp;\@ref(fig:multiverseresultsdrugs) - here, we only show models that were not found to have immediate problems representing the data well or computational issues. Results for all models we tested are reported in  supplementary Figures `r supplementary_figures_multiverse`, with additional details in supplementary statistical analysis. The results do not change noticeably when only patients from the first wave are included (supplementary Figures `r supplementary_figures_multiverse`).

@@

## Prognostic models are not better than just using age

@@

```{r riskscores, fig.cap="Performance of tested prediction scores as measured by AUC. AUC = 1 means perfect prediction while AUC $\\leq$ 0.5 means that the score is worse than random guess and a better prediction would be obtained by reversing the score (marked by thick blue line). The line ranges represent the bootstrapped 95% confidence intervals. Red dots show results computed in present study - individual dots vary in the outcome measured (12-day or 30-day mortality) and potentially on how ambiguities in score computation were resolved, although this rarely makes a big difference. Cyan triangles show AUC as reported by the original authors or recomputed based on their published data. When the confidence interval or the AUC of the original study is not shown, it means that the value was not reported by the authors and not enough information to recompute it was given."}
col_types_auc <- cols(
  auc = col_double(),
  auc_low = col_double(),
  auc_high = col_double(),
  outcome = col_character(),
  score = col_character(),
  note = col_character(),
  subgroup = col_character()
)
all_auc <- read_csv(here::here("manuscript", "all_auc.csv"), col_types = col_types_auc, na = "NA") %>% filter(subgroup != "(admission)")
all_auc_orig <- read_csv(here::here("manuscript", "all_auc_orig.csv"), col_types = col_types_auc, na = "NA") %>% filter(subgroup != "(admission)")

>>>>

---
title: "Detailed disease progression of 213 patients hospitalized with Covid-19 in the Czech Republic: An exploratory analysis" 
output: 
  #rticles::arxiv_article
  #pdf_document
  # bookdown::pdf_document2:
  #    toc: false
  bookdown::word_document2: 
    toc: false
    number_sections: false
    reference_docx: "output_template.docx"
abstract: |  
  **Abstract:** We collected a multi-centric retrospective dataset of patients (N = 213) who were admitted to ten hospitals in Czech Republic and tested positive for SARS-CoV-2. The dataset contains baseline patient characteristics, breathing support required, pharmacological treatment received and multiple markers on daily resolution. Patients in the dataset were treated with hydroxychloroquine (N = 108), azithromycin (N = 72), favipiravir (N = 9), convalescent plasma (N = 7), dexamethasone (N = 4) and remdesivir (N = 3), often in combination. Most patients were admitted during the first wave of the epidemic. To explore association between treatments and patient outcomes we performed multiverse analysis, observing how the conclusions change between defensible choices of statistical model, predictors included in the model and other analytical degrees of freedom.  Weak evidence to constrain the potential efficacy of azithromycin and favipiravir can be extracted from the data. Additionally, we performed external validation of several proposed prognostic models for Covid-19 severity showing that they mostly perform unsatisfactorily on our dataset.
bibliography: Covid19.json
csl: journal-of-medical-virology.csl
date: "Version: `r format(Sys.time(), '%Y-%m-%d')`"
author: "`r { source(here::here('manuscript', 'authors.R')); get_authors_string() }`"
---

@@

The Covid-19 pandemic caused by severe acute respiratory syndrome coronavirus (SARS-CoV-2) has, as of November 2020, led to over 46 million cases and over 1.1 million deaths. Proposed treatments include antivirals approved for other indications (chloroquine, hydroxychloroquine, lopinavir/ritonavir, remdesivir, favipiravir, umifenovir), azithromycin, corticosteroids, immunoglobulins, tocilizumab and convalescent plasma [@http://zotero.org/users/5567156/items/8XWTUMUI; @http://zotero.org/users/5567156/items/6Q8Z8VJR]. As of this writing, the only treatment that exhibited positive effects in randomized trials is the corticosteroid dexamethasone for severe cases [@http://zotero.org/users/5567156/items/IW6VZ53Q; @http://zotero.org/users/5567156/items/5VAKEW58]. Remdesivir, previously designed and approved for Ebola, SARS and MERS, is currently the only antiviral against SARS-CoV-2 approved by the FDA. However, during spring and summer it was available only in limited amounts via compassionate use programme. Randomized clinical trials on remdesivir have provided  conflicting evidence [@http://zotero.org/users/5567156/items/MFS3IPPU; @http://zotero.org/users/5567156/items/KB5UDZH3]. Despite initial promise, hydroxychloroquine has failed to show benefit for hospitalized patients [@http://zotero.org/users/5567156/items/9X3UH8ZM; @http://zotero.org/users/5567156/items/KB5UDZH3], as an early treatment [@http://zotero.org/users/5567156/items/G6KZKVMI], as well as pre- and post-exposure prophylaxis [@http://zotero.org/users/5567156/items/7C23YCV5; @http://zotero.org/users/5567156/items/GMR9FX9Z; @http://zotero.org/users/5567156/items/H4CLJNUR]. Further, no improvement could be discerned when adding azithromycin to hydroxychloroquine therapy [@http://zotero.org/users/5567156/items/BQLRZGTQ]. Similarly, Lopinavir/Ritonavir did not show benefit [@http://zotero.org/users/5567156/items/6I6GAVWU]. No benefit was observed for convalescent plasma [@http://zotero.org/users/5567156/items/UEXLDJCB; @http://zotero.org/users/5567156/items/BHGT88US].

@@

Favipiravir is one of the less explored experimental treatments, previously used for influenza including avian types, with only one larger RCT in Covid- 19 known to us [@http://zotero.org/users/5567156/items/ISLSL7UC], the study however has many potentially severe problems [@http://zotero.org/users/5567156/items/7HDXLWEA]. Other studies are scarce - even when considering very small studies and case series [@http://zotero.org/users/5567156/items/F3VNTQ92; @http://zotero.org/users/5567156/items/FSUQMUP8; @http://zotero.org/users/5567156/items/894H9N9B]. None of the results allow strong conclusions about benefits or harms of favipiravir, although a  metaanalysis of all available small studies showed an effect of favipiravir on clinical improvement in mild and moderate disease [@http://zotero.org/users/5567156/items/7595KBWR].

 For additional summary of treatments under investigation see Siemieniuk et al. [@http://zotero.org/users/5567156/items/YP62P6XJ]

@@

```{r progression, fig.cap="Disease progression for all patients included in the study as determined by breathing support required. Each horizontal strip is a single patient, the ordering on the vertical axis is by disease severity, the split into two panels is for visual purposes only. Ventilated = any form of ventilation (non-invasive positive-pressure ventilation, mechanical ventilation and extra-corporeal membrane oxygenation)."}
my_paste <- function(x) {
  paste0(as.integer(x), collapse = "")
}

@@

As noted above, the nature of the convenience sample did not enforce random assignment of treatments to patients. In fact, patients with worse baseline characteristics, which lead to worse outcomes, were less likely to receive hydroxychloroquine (see Supplementary Figure 2). This clearly creates a bias towards a positive effect of hydroxychloroquine on the outcome (and potentially for other treatments as well - most were used in combination with hydroxychloroquine), which, however, could be false.

@@

Here, we focus on hydroxychloroquine and azithromycin as those are the only treatments with larger sample size. We also investigate favipiravir as it is less well reported in the literature. Hydroxychloroquine was dosed almost exclusively in a 5-day regime starting with a loading dose of 800mg on the first day and followed by 400mg. Majority of patients complemented hydroxychloroquine with azithromycin while azithromycin was rarely used alone (see Table \@ref(tab:summarytable)). Azithromycin was most frequently dosed 250 or 500mg/day, but doses ranging from 100mg/day to 1500 mg/day were observed.  Favipiravir was used only at one site with a loading dose of 3600mg on the first day, followed by at most 9 days with a 1600mg dose. All but one of the patients receiving favipiravir also received hydroxychloroquine. Treatment was initiated mostly within two days of admission (see Supplementary Figure 3).

The results of the multiverse analysis for association between hydroxochloroquine, azithromycin and favipiravir usage and death is shown in Figure&nbsp;\@ref(fig:multiverseresultsdrugs) - here, we only show models that were not found to have immediate problems representing the data well or computational issues (see Supplementary statistical analysis for details). Results for all models we tested are reported in  supplementary Figures `r supplementary_figures_multiverse`, with additional details in supplementary statistical analysis. The results do not change noticeably when only patients from the first wave are included (supplementary Figures `r supplementary_figures_multiverse`).

@@

## Published prognostic models are not better than using age as the sole predictor of outcome

@@

```{r riskscores, fig.cap="Performance of tested prediction scores as measured by AUC. AUC = 1 means perfect prediction while AUC $\\leq$ 0.5 means that the score is worse than random guess and a better prediction would be obtained by reversing the score (marked by thick blue line). The line ranges represent the bootstrapped 95% confidence intervals. Red dots show results computed in present study - model variants (horizontal axis) vary in the outcome measured (12-day or 30-day mortality, severe disease) and potentially on how ambiguities in score computation were resolved, although this rarely makes a big difference - see supplementary statistical analysis for details. Cyan triangles show AUC as reported by the original authors or recomputed based on their published data. When the confidence interval or the AUC of the original study is not shown, it means that the value was not reported by the authors and not enough information to recompute it was given."}
col_types_auc <- cols(
  auc = col_double(),
  auc_low = col_double(),
  auc_high = col_double(),
  outcome = col_character(),
  score = col_character(),
  note = col_character(),
  subgroup = col_character()
)
all_auc <- read_csv(here::here("manuscript", "all_auc.csv"), col_types = col_types_auc, na = "NA") %>% filter(subgroup != "(admission)")
all_auc_orig <- read_csv(here::here("manuscript", "all_auc_orig.csv"), col_types = col_types_auc, na = "NA") %>% filter(subgroup != "(admission)")

### 2020-12-02 manuscript/risk_scores.Rmd
Jm and risks for supplement
Version as sent for approval to co-authors
More tweaks from feedback

```{r setup, echo=FALSE, message=FALSE, warning = FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE)

@@

# ACP

@@

# Chen and Liu

@@

# Shi et al.

@@

# Caramelo et al.

@@

# Bello-Chavolla et al.

@@

# Age only

@@

# All together now

```{r, fig.cap = "The AUC and it's 95% credible intervals for all of the scores considered so far. The thick blue line marks AUC of 0.5, i.e. the point where reverting the score would yield better predictions. The thin gray dashed line marks the AUC from the original study for easier comparison."}

@@

# References

>>>>

# Validating published prognostic models

```{r setup_risk_scores, echo=FALSE, message=FALSE, warning = FALSE, results = "hide"}
knitr::opts_chunk$set(echo = FALSE)

@@

## ACP

@@

## Chen and Liu

@@

## Shi et al.

@@

## Caramelo et al.

@@

## Bello-Chavolla et al.

@@

## Age only

@@

## Summary

```{r, fig.cap = "The AUC and it's 95% credible intervals for all of the scores considered so far. The thick blue line marks AUC of 0.5, i.e. the point where reverting the score would yield better predictions. The thin gray dashed line marks the AUC from the original study for easier comparison.", fig.width = 8, fig.height=6}

@@

### 2020-12-02 manuscript/supplementary_figures.Rmd
More tweaks from feedback

@@

models<-list(m.ihd,m.hd,m.hf,m.copd,m.asthma,m.old,m.dia,m.rd,m.ld,m.s,m.ob,m.hc,m.hi,m.la)
modelNames<-c('IHD','HD','HF','COPD','Asthma','LungD','Dia','RenalD','LiverD','Smoking','Obesity','HighCr','HighInr','LowAlb')
ys<-c(0)
for (m in models) {
  ys<-c(min(min(ys),confint(m)[2,1]),max(max(ys),confint(m)[2,2]))
}
models2<-list(m2.ihd,m2.hd,m2.hf,m2.copd,m2.asthma,m2.old,m2.dia,m2.rd,m2.ld,m2.s,m2.ob,m2.hc,m2.hi,m2.la)
modelNames2<-modelNames
ys2<-c(0)
for (m in models2) {
  ys2<-c(min(min(ys2),confint(m)[2,1]),max(max(ys2),confint(m)[2,2]))
}

plot(ys,c(1,length(modelNames)),ty='n',yaxt='n',xlab='Log odds ratio',ylab='')
abline(v=0,col='blue')
col.hcq<-bfc()["Vermillion"]
for (i in seq(along=models)) {
  ii<-length(models)-i+1
  m<-models[[i]]
  m2<-models2[[i]]
  lines(confint(m)[2,],rep(ii,2))
  points(coef(m)[2],ii,pch=19)
  lines(-confint(m2)[2,],rep(ii,2)-.3,col=col.hcq)
  points(-coef(m2)[2],ii-.3,col=col.hcq,pch=19)
}
axis(2,length(modelNames):1,modelNames,las=2)
legend('right',c('Death','No HCQ'),lty=1,col=c('black',col.hcq))
```

@@

```{r allmultaz, fig.height=11, fig.cap = "Estimates of model coefficients for association between azithromycin and main outcomes. The \"Suspicious\" section shows models that were found to not fit the data well or have computational issues - see supplementary statistical analysis for details.  Each row represents a model - Categorical All/7/28 = Bayesian categorical regression for state at last observed day/day 7/day 28, Binary All/7/28 = Bayesian logistic regression for state at last observed day/day 7/day 28, Bayes Cox = Bayesian version of the Cox proportional hazards model with a binary outcome, Cox (single) = frequentist Cox model with a binary outcome, Cox (competing) = frequentist Cox model using competing risks (as in Figure 1a), HMM A = Bayesian hidden-Markov model as in Figure 1b with predictors for rate groups, HMM B = Bayesian hidden-markov model as in Figure 1b with predictors for individual rates, HMM C = Bayesian hidden-Markov model as in Figure 1c. For frequentist models, we show maximum likelihood estimate and 95% confidence interval, for Bayesian models we show posterior mean and 95% credible interval. The estimands are either log odds-ratio (Categorical, HMM) or log hazard ratio (Cox variants) or log ratio of mean duration of hospitalization (HMM duration). In all cases coefficient < 0 means better patient outcome in the treatment group. Vertical lines indicate zero (blue) and substantial increase or decrease with odds or hazard ratio of 3:2 or 2:3 (green). Additionally the factors the model adjusted for are listed - Site = the study site, admitted = Admitted for Covid-19, Supportive = best supportive care initiated, Comorb. = total number of comorbidities, AZ = took azithromycin, HCQ = took hydroxychloroquine, FPV = took favipiravir, C. plasma = received convalescent plasma, first wave = only patients admitted before September 1st were included. "}
plot_multiverse(read_all_multiverse_res() %>% filter(grepl("az", hypothesis)), show_check = TRUE)

@@

```{r allmultfpv, fig.height=11, fig.cap = "Estimates of model coefficients for association between favipiravir and main outcomes. The \"Suspicious\" section shows models that were found to not fit the data well or have computational issues - see supplementary statistical analysis for details.  Each row represents a model - Categorical All/7/28 = Bayesian categorical regression for state at last observed day/day 7/day 28, Binary All/7/28 = Bayesian logistic regression for state at last observed day/day 7/day 28, Bayes Cox = Bayesian version of the Cox proportional hazards model with a binary outcome, Cox (single) = frequentist Cox model with a binary outcome, Cox (competing) = frequentist Cox model using competing risks (as in Figure 1a), HMM A = Bayesian hidden-Markov model as in Figure 1b with predictors for rate groups, HMM B = Bayesian hidden-markov model as in Figure 1b with predictors for individual rates, HMM C = Bayesian hidden-Markov model as in Figure 1c. For frequentist models, we show maximum likelihood estimate and 95% confidence interval, for Bayesian models we show posterior mean and 95% credible interval. The estimands are either log odds-ratio (Categorical, HMM) or log hazard ratio (Cox variants) or log ratio of mean duration of hospitalization (HMM duration). In all cases coefficient < 0 means better patient outcome in the treatment group. Vertical lines indicate zero (blue) and substantial increase or decrease with odds or hazard ratio of 3:2 or 2:3 (green). Additionally the factors the model adjusted for are listed - Site = the study site, admitted = Admitted for Covid-19, Supportive = best supportive care initiated, Comorb. = total number of comorbidities, AZ = took azithromycin, HCQ = took hydroxychloroquine, FPV = took favipiravir, C. plasma = received convalescent plasma, first wave = only patients admitted before September 1st were included. "}
plot_multiverse(read_all_multiverse_res() %>% filter(grepl("favipiravir", hypothesis), model_check != "Problematic"), show_check = TRUE)

```{r multiverseresultsmarkers, fig.height=3.5, fig.width=8.5, fig.cap="Estimates of model coefficients (log hazard ratios) for association between markers and death. The \"Suspicious\" section shows models that were found to not fit the data well or have computational issues, \"Problematic\" section shows models that were completely broken - see supplementary statistical analysis for details. Each row represents a model - Cox (competing) =  frequentist Cox model using competing risks (as in Figure 1a), HMM A = Bayesian hidden-markov model as in Figure 1b with predictors for rate groups, JM = Bayesian joint longitudinal and time-to-event model. For frequentist models, we show maximum likelihood estimate and 95% confidence interval, for Bayesian models we show posterior mean and 95% credible interval. Additionally the factors the model adjusted for are listed - Site = the study site, Supportive = best supportive care initiated, HCQ = took Hydroxychloroquine. We show posterior mean and 95% credible interval."}
plot_multiverse(read_all_multiverse_res() %>% filter(group == "markers"), adjustments_to_hide = c("admitted", "smoking", "obesity", "comorbidities \\(sum\\)", "az", "favipiravir", "convalescent_plasma"), show_check = TRUE)

>>>>

models<-list(m.ihd,m.hd,m.hf,m.copd,m.asthma,m.old,m.dia,m.rd,m.ld,m.s,m.ob,m.hc,m.hi,m.la)
models2<-list(m2.ihd,m2.hd,m2.hf,m2.copd,m2.asthma,m2.old,m2.dia,m2.rd,m2.ld,m2.s,m2.ob,m2.hc,m2.hi,m2.la)
modelNames<-c('IHD','HD','HF','COPD','Asthma','LungD','Dia','RenalD','LiverD','Smoking','Obesity','HighCr','HighInr','LowAlb')
gtmp<-c()
for (i in rev(seq(along=models))) {
  ii<-length(models)-i+1
  m<-models[[i]]
  m2<-models2[[i]]
  ci<-confint(m)[2,]
  ci2<-confint(m2)[2,]
  gtmp<-rbind(gtmp,data.frame(est=coef(m)[2],low=ci[1],high=ci[2],name=modelNames[i],type='outcome'))
  gtmp<-rbind(gtmp,data.frame(est=-coef(m2)[2],low=-ci2[1],high=-ci2[2],name=modelNames[i],type='hcq'))
}
ggplot(gtmp,aes(y=name,x=est,xmin=low,xmax=high,color=type))+
  geom_vline(xintercept=0,color='blue')+
  geom_point(position=position_dodge(width=0.5))+
  geom_errorbarh(position=position_dodge(width=0.5),height= 0.5)+
  scale_x_continuous('Log odds ratio')+
  scale_y_discrete('')+
  scale_color_manual('Model of:',values=c('black','red'),labels=c('Death','No HCQ'))+
  theme(legend.background = element_rect(fill="gray95"),legend.position=c(.83,.7))
```

@@

@@

```{r allmultaz, fig.height=11, fig.cap = "Estimates of model coefficients for association between azithromycin and main outcomes. The \"Suspicious\" section shows models that were found to not fit the data well or have computational issues - see supplementary statistical analysis for details.  Each row represents a model - Categorical All/7/28 = Bayesian categorical regression for state at last observed day/day 7/day 28, Binary All/7/28 = Bayesian logistic regression for state at last observed day/day 7/day 28, Bayes Cox = Bayesian version of the Cox proportional hazards model with a binary outcome, Cox (single) = frequentist Cox model with a binary outcome, Cox (competing) = frequentist Cox model using competing risks (as in Figure 1a), HMM A = Bayesian hidden-Markov model as in Figure 1b with predictors for rate groups, HMM B = Bayesian hidden-markov model as in Figure 1b with predictors for individual rates, HMM C = Bayesian hidden-Markov model as in Figure 1c. For frequentist models, we show maximum likelihood estimate and 95% confidence interval, for Bayesian models we show posterior mean and 95% credible interval. The estimands are either log odds-ratio (Categorical, HMM) or log hazard ratio (Cox variants) or log ratio of mean duration of hospitalization (HMM duration). In all cases coefficient < 0 means better patient outcome in the treatment group. Vertical lines indicate zero (blue) and substantial increase or decrease with odds or hazard ratio of 3:2 or 2:3 (green). Additionally the factors the model adjusted for are listed - Site = the study site, admitted = Admitted for Covid-19, Supportive = best supportive care initiated, Comorb. = total number of comorbidities, AZ = took azithromycin, HCQ = took hydroxychloroquine, FPV = took favipiravir, C. plasma = received convalescent plasma, first wave = only patients admitted before September 1st were included. "}
plot_multiverse(read_all_multiverse_res() %>% filter(grepl("az", hypothesis)), show_check = TRUE)
```

```{r allmultfpv, fig.height=11, fig.cap = "Estimates of model coefficients for association between favipiravir and main outcomes. The \"Suspicious\" section shows models that were found to not fit the data well or have computational issues - see supplementary statistical analysis for details.  Each row represents a model - Categorical All/7/28 = Bayesian categorical regression for state at last observed day/day 7/day 28, Binary All/7/28 = Bayesian logistic regression for state at last observed day/day 7/day 28, Bayes Cox = Bayesian version of the Cox proportional hazards model with a binary outcome, Cox (single) = frequentist Cox model with a binary outcome, Cox (competing) = frequentist Cox model using competing risks (as in Figure 1a), HMM A = Bayesian hidden-Markov model as in Figure 1b with predictors for rate groups, HMM B = Bayesian hidden-markov model as in Figure 1b with predictors for individual rates, HMM C = Bayesian hidden-Markov model as in Figure 1c. For frequentist models, we show maximum likelihood estimate and 95% confidence interval, for Bayesian models we show posterior mean and 95% credible interval. The estimands are either log odds-ratio (Categorical, HMM) or log hazard ratio (Cox variants) or log ratio of mean duration of hospitalization (HMM duration). In all cases coefficient < 0 means better patient outcome in the treatment group. Vertical lines indicate zero (blue) and substantial increase or decrease with odds or hazard ratio of 3:2 or 2:3 (green). Additionally the factors the model adjusted for are listed - Site = the study site, admitted = Admitted for Covid-19, Supportive = best supportive care initiated, Comorb. = total number of comorbidities, AZ = took azithromycin, HCQ = took hydroxychloroquine, FPV = took favipiravir, C. plasma = received convalescent plasma, first wave = only patients admitted before September 1st were included. "}
plot_multiverse(read_all_multiverse_res() %>% filter(grepl("favipiravir", hypothesis), model_check != "Problematic"), show_check = TRUE)
```

```{r multiverseresultsmarkers, fig.height=5, fig.width=8.5, fig.cap="Estimates of model coefficients (log hazard ratios) for association between markers and death. The \"Suspicious\" section shows models that were found to not fit the data well or have computational issues, \"Problematic\" section shows models that were completely broken - see supplementary statistical analysis for details. Each row represents a model - Cox (competing) =  frequentist Cox model using competing risks (as in Figure 1a), HMM A = Bayesian hidden-markov model as in Figure 1b with predictors for rate groups, JM = Bayesian joint longitudinal and time-to-event model. For frequentist models, we show maximum likelihood estimate and 95% confidence interval, for Bayesian models we show posterior mean and 95% credible interval. Additionally the factors the model adjusted for are listed - Site = the study site, Supportive = best supportive care initiated, HCQ = took Hydroxychloroquine. We show posterior mean and 95% credible interval."}
plot_multiverse(read_all_multiverse_res() %>% filter(group == "markers"), adjustments_to_hide = c("admitted", "smoking", "obesity", "comorbidities \\(sum\\)", "az", "favipiravir", "convalescent_plasma"), show_check = TRUE)

@@
